\chapter*{}



\hskip7mm



\begin{center}
\section*{Acknowledgement}

\end{center}

\begin{spacing}{1.3}
This dissertation was made possible through the patience and guidance of my advisor, \textbf{Mrs. Lobna Jribi}. I am most grateful for her constant support and encouragements that brought my work in the right direction.\\

I would like to thank also my beloved family for their continuous encouragement, support and help in every step that I make. You provide me the strength that I need to go forward.\\

I would also like to thank the members of the jury for taking the time to evaluate my work and give me valuable feedback.\\

Kind regards go to my internship supervisors and collaborators: \textbf{Mr. Mohamed Anis Mlaouah}, \textbf{Mr. Mohamed Mehdi Sidommou} and \textbf{Mrs. Imen Majed}. I am grateful for giving me the chance to work with you and for all your mentoring advices. You have all helped me to improve my work and myself.\\

I would also like to thank a number of friends that were particularly supportive along this path. All my gratitude to my \textbf{National School of Computer Sciences} classmates. Many thanks to my \textbf{Preparatory Institute for Engineering Studies-El Manar} classmates with whom I closely shared many enlightening experiences during two years of preparatory studies.\\

Finally, many thanks to all other people that had a direct or indirect contribution to this work and were not explicitly mentioned above. Your help and support is very much appreciated.\\
\end{spacing}
