\chapter*{Conclusion} 
\addcontentsline{toc}{chapter}{Conclusion}

As we are in the data era, data analysis has become one of the crucial computer sciences fields. Challenges beyond data analysis are growing more and more, and providing exploitable results from processing a large scale of data has become a priceless fortune for data owners.\\

The aim of this final graduation project is to design a suitable solution to process huge amount of data in order to run data mining algorithm without falling in the matter of slow data processing or out of memory issues, and to implement a graphical user interface that make it easy for costumers to visualize meaningful results.\\

Throughout this report, we have detailed the different phases of our project's life cycle starting with a preliminary study in which we defined some useful concepts then we have examined existent solution to our problem. Following, was the requirements specification where we have presented our application needs through functional and non-functional requirements. Then, we have focused on the design stage by elaborating class and sequence diagrams. Finally, we have proceeded to the implementation phase where we have exposed the achieved work.\\

Throughout this project, we faced various challenges related to the design of an advanced architecture and adapting it to big data manufacturing tools, in the search of the best possible performance. Merge from the desktop first prototype to a web based solution was also a challenge during this project, and it was made through separating executing components in our architecture.\\

For the next release, many extensions are expected to be added to our current solution. Indeed, we can add more data mining algorithms to our application and use the provided results to offer more expressive visualization for our application costumers. Nodes and clusters are also an important component of our system performance for either storage or processing data. Thus, improvements can cover this level also. 

